`forestecology` package for modeling interspecies competition between trees

### 2021-01-09 etc/paper/forestecology.Rmd
first pass of cleaning and abstract

1. set the context for and purpose of the work 
1. indicate the approach and the methods 
1. outline the main results 
1. identify the conclusions and wider implications

@@

```{r bw-define-cv-folds-with-trees, out.width="100%", fig.cap="Inspect blocks closely."}
# Visualize grid. Why does fold 19 repeat?
ggplot() +
  geom_sf(data = bw_spatialBlock$blocks %>% st_as_sf()) + 
  geom_sf(data = bw_growth_df %>% sample_frac(0.2), 
          aes(col = factor(foldID)), size = 0.1) + 
  theme(legend.position="bottom")
```

>>>>

1. set the context for and purpose of the work: models for interspecific competition. Robert and spatial crossvalidation 
1. indicate the approach and the methods: use tidyverse, sf, and tidymodels packages. 
1. outline the main results: Recreate the figure in PLOSOne paper. Code would've been way more complicated in base. We don't have to worry about how the component functions work, only that sequence/converyor belt is correct and output is correct. scientist is abstracted away from ugly programming details.
1. identify the conclusions and wider implications: the fact truths hold was already covered in PLOSOne paper, this package implements this and can serve as a blueprint for others who model

@@

```{r bw-define-cv-folds-with-trees, out.width="100%", fig.cap="Inspect blocks closely."}
# Visualize grid. Why does fold 19 repeat?
ggplot() +
  geom_sf(data = bw_spatialBlock$blocks %>% st_as_sf()) + 
  geom_sf(data = bw_growth_df %>% sample_frac(0.2), 
          aes(col = factor(foldID)), size = 0.1, show.legend = FALSE) + 
  geom_sf_text(data = bw_spatialBlock$blocks %>% st_as_sf(), 
               aes(label = folds))
```
